Step 14: Export All Results

### 2025-09-08 reanalysis-13-forest_plots.qmd
reorganize

# Configuration
marginal_effects_dir <- file.path(reanalysis_data_dir, "marginal_effects_cache")
pooled_cache_dir <- file.path(reanalysis_data_dir, "ps_cache", "pooled_results")
plots_dir <- file.path(reanalysis_data_dir, "forest_plots")

@@

```{r load-data}
# Load marginal effects results
mfx_results_file <- file.path(marginal_effects_dir, "pooled_mfx_results.rds")
if (file.exists(mfx_results_file)) {
  pooled_mfx <- readRDS(mfx_results_file)
  cat("✓ Loaded marginal effects results\n")
} else {
  cat("✗ Marginal effects results not found. Run reanalysis-13 first.\n")
  pooled_mfx <- list()
}

>>>>

# Configuration
marginal_effects_dir <- file.path(reanalysis_data_dir, "marginal_effects")
pooled_cache_dir <- file.path(reanalysis_data_dir, "ps_cache", "pooled_results")
plots_dir <- file.path(reanalysis_data_dir, "forest_plots")

@@

```{r load-data}
# Load marginal effects results
mfx_results_file <- file.path(marginal_effects_dir, "pooled_mfx_results.rds")
if (file.exists(mfx_results_file)) {
  pooled_mfx <- readRDS(mfx_results_file)
  cat("✓ Loaded marginal effects results\n")
} else {
  cat("✗ Marginal effects results not found. Run reanalysis-12-marginal_effects.qmd first.\n")
  pooled_mfx <- list()
}

### 2025-09-08 reanalysis-14-export_results.qmd
reorganize

# Configuration
pooled_cache_dir <- file.path(reanalysis_data_dir, "ps_cache", "pooled_results")
marginal_effects_dir <- file.path(reanalysis_data_dir, "marginal_effects_cache")
forest_plots_dir <- file.path(reanalysis_data_dir, "forest_plots")
export_dir <- file.path(reanalysis_data_dir, "exported_results")

>>>>

# Configuration
pooled_cache_dir <- file.path(reanalysis_data_dir, "ps_cache", "pooled_results")
marginal_effects_dir <- file.path(reanalysis_data_dir, "marginal_effects")
forest_plots_dir <- file.path(reanalysis_data_dir, "forest_plots")
export_dir <- file.path(reanalysis_data_dir, "exported_results")
